The Rockerverse: Packages and Applications for Containerisation with R

### 2020-03-03 README.Rmd
rename main file to something meaningful
following submission guidelines

```bash
docker build --tag rockerverse-paper --file .binder/Dockerfile .
docker run -i -v $(pwd):/rockerverse --user $UID rockerverse-paper Rscript -e 'setwd("/rockerverse"); rmarkdown::render("manuscript.Rmd")'
```

@@

```bash
docker run -i -v $(pwd):/rockerverse --user $UID nuest/rockerverse-paper Rscript -e 'setwd("/rockerverse"); rmarkdown::render("manuscript.Rmd")'
```

>>>>

```bash
docker build --tag rockerverse-paper --file .binder/Dockerfile .
docker run -i -v $(pwd):/rockerverse --user $UID rockerverse-paper Rscript -e 'setwd("/rockerverse"); rmarkdown::render("rockerverse.Rmd")'
```

@@

```bash
docker run -i -v $(pwd):/rockerverse --user $UID nuest/rockerverse-paper Rscript -e 'setwd("/rockerverse"); rmarkdown::render("rockerverse.Rmd")'
```

### 2020-03-03 rockerverse.Rmd
rename main file to something meaningful
following submission guidelines

```{r word_stats, eval=FALSE, include=FALSE}
# devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)
wordcountaddin::readability(here::here("manuscript.Rmd"))
wordcountaddin::text_stats(here::here("manuscript.Rmd"))
```

@@

rmarkdown::render("manuscript.Rmd", output_format = rjournal_style_preprint())
file.rename("RJwrapper.pdf", "rockerverse-preprint.pdf") # file for own archival

# For submission to arXiv:
# 1. Copy the following files into a new folder:
# - figures/*
# - manuscript.tex
# - RJournal.sty
# - RJreferences.bib
# - RJwrapper.tex
# 2. Run pdfLaTeX directly on RJwrapper.tex (works with RStudio)
# 3. Zip the following files and submit to arXiv:
# - /figures
# - manuscript.tex
# - RJournal.sty
# - RJwrapper.bbl
# - RJwrapper.tex
```

```{r collab_emails, eval=FALSE, include=FALSE}
front_matter <- rmarkdown::yaml_front_matter("manuscript.Rmd")
emails <- sapply(X = front_matter$author, FUN = function(a) { a$email })
cat(emails, sep = "\n")
```

```{bash collab_handles, eval=FALSE, include=FALSE}
cat manuscript.Rmd | grep '    # https://github.com/' | sed 's|    # https://github.com/|@|'
```

>>>>

```{r word_stats, eval=FALSE, include=FALSE}
# devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)
wordcountaddin::readability(here::here("rockerverse.Rmd"))
wordcountaddin::text_stats(here::here("rockerverse.Rmd"))
```

@@

rmarkdown::render("rockerverse.Rmd", output_format = rjournal_style_preprint())
file.rename("RJwrapper.pdf", "rockerverse-preprint.pdf") # file for own archival

# For submission to arXiv:
# 1. Copy the following files into a new folder:
# - figures/*
# - rockerverse.tex
# - RJournal.sty
# - RJreferences.bib
# - RJwrapper.tex
# 2. Run pdfLaTeX directly on RJwrapper.tex (works with RStudio)
# 3. Zip the following files and submit to arXiv:
# - /figures
# - rockerverse.tex
# - RJournal.sty
# - RJwrapper.bbl
# - RJwrapper.tex
```

```{r collab_emails, eval=FALSE, include=FALSE}
front_matter <- rmarkdown::yaml_front_matter("rockerverse.Rmd")
emails <- sapply(X = front_matter$author, FUN = function(a) { a$email })
cat(emails, sep = "\n")
```

```{bash collab_handles, eval=FALSE, include=FALSE}
cat rockerverse.Rmd | grep '    # https://github.com/' | sed 's|    # https://github.com/|@|'
```
